---
title: "Project 10"
author: "Ibrahim All-Mamun"
date: "2025-12-11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
library(tidyverse)
library(gt)
library(gtsummary)

library(haven)
library(stringr)
library(flextable)
library(officer)
library(summarytools)
library(openxlsx)

library(forcats)

library(dplyr)
library(survival)
library(survminer)

library(labelled)

library(mice)
library(jomo)

select <- dplyr::select
source("codes.R")
```



```{r}
df <- read.xlsx("Data/data.xlsx", 1)
names(df)
```

```{r}
names(df) <- varNames
```


```{r}
table(df$age)
```


# Data
```{r}
read.xlsx("Data/data.xlsx", 1) -> df

names(df) <- varNames

df <- df[sample(nrow(df), 270), ]


# Convert characters to factors
df <- df %>%
  mutate(
    age_group = case_when(
      age %in% 18:25 ~ "18–25",
      age %in% 26:35 ~ "26–35",
      age >  35      ~ "35+",
      TRUE           ~ NA_character_
    ),
    age_group = factor(age_group, levels = c("18–25", "26–35", "35+")),  # ordered levels
    pain_severity_score = case_when(
      pain_severity_score %in% 0:3 ~ "0–3",
      pain_severity_score %in% 4:6 ~ "4–6",
      pain_severity_score >  6     ~ "7-9",
      TRUE           ~ NA_character_
    ),
    pain_severity_score = factor(pain_severity_score, levels = c("0–3", "4–6", "7-9"))  # ordered levels
  ) %>%
  mutate(across(where(is.character), as.factor))

df %>%
  set_variable_labels(
    age = "Age",
    age_group = "Age",
    marital = "Marital status",
    education = "Education level",
    household_income = "Monthly household income",
    residence = "Place of residence",
    duration_living = "Duration living in Dhaka years",
    duration_working = "Duration working construction",
    primary_job = "Primary job task",
    working_hr_day = "Working hours per day",
    working_hr_week = "Working days per week",
    workplace_toilet = "Workplace toilet availability",
    workplace_water = "Workplace drinking water access",
    age_menarche = "Age at menarche years",
    menstrual_regularity = "Menstrual cycle regularity",
    duration_menstrual = "Duration of menstrual period days",
    missed_menstrual = "Missed menstrual period last 6 months",
    absorbent_type = "Type of absorbent used",
    afford_pads = "Afford sanitary pads",
    pain_experience = "Menstrual pain experience",
    pain_severity_score = "Menstrual pain severity score",
    frequency_of_pain = "Frequency of menstrual pain",
    reduced_work = "Missed or reduced work due to menstrual pain",
    pain_urination = "Burning or pain during urination",
    frequent_urination = "Frequent or urgent urination",
    lower_abdominal_pain = "Lower abdominal pain or discomfort",
    lower_back_pain = "Lower back or flank pain",
    bloody_urine = "Cloudy dark or bloody urine",
    vaginal_discharge = "Abnormal vaginal discharge",
    vaginal_odor = "Foul smelling vaginal odor",
    genital_itching = "Genital itching or irritation",
    pain_intercourse = "Pain or discomfort during sexual intercourse",
    reduced_fluid_intake = "Reduced fluid intake during work",
    urination_frequency = "Frequency of urination during work",
    urination_delay = "Delaying urination at work",
    symptoms = "Sought medical care for urinary or reproductive symptoms",
    reasons = "Reasons for not seeking care",
    place_care = "Place of seeking care",
    time_care = "Time taken to seek care",
    satisfaction = "Satisfaction with healthcare services",
    received_treatment = "Received medication or treatment"
  ) -> df



```
# Helper: build one tbl_summary per dependent variable
```{r}
make_bivariate_tbl <- function(data, dep_var, ind_var) {
  data %>%
    select(
      all_of(ind_var),
      all_of(dep_var)
    ) %>%
    tbl_summary(
      by = all_of(dep_var),
      statistic = list(
        all_continuous()  ~ "{mean} ± {sd}",
        all_categorical() ~ "{n} ({p}%)"
      ),
      digits  = all_continuous() ~ 1,
      missing = "no"
    ) %>%
    add_p(
      test = list(
        all_continuous()  ~ "t.test",
        all_categorical() ~ "chisq.test"
      ),
      pvalue_fun = ~ style_pvalue(.x, digits = 3)
    ) %>%
    bold_p(t = 0.05) %>%
    modify_spanning_header(
      all_stat_cols() ~ paste0("**", var_label(df[,dep_var]), "**")
    ) %>%
    modify_header(label ~ "**Variable**") %>% 
    suppressMessages
}


```

# Descriptive Tables
```{r}
tbl <- df %>%
  select(
    age_group,
    marital,
    education,
    household_income,
    residence,
    duration_living,
    duration_working
  ) %>%
  tbl_summary(
    statistic = list(
      all_continuous()  ~ "{mean} ± {sd}",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits  = all_continuous() ~ 1,
    missing = "no"
  ) %>%
  suppressMessages %>% 
  as_flex_table
```


```{r}
doc <- read_docx() 

doc <- doc %>% 
  body_add_par(value = "Job and Working Hour Related") %>%
  body_add_flextable(value = tbl) %>% 
  body_add_par(value = "")
```


## Job and Working Hour Related
```{r}
ind_var <- c("primary_job",
             "working_hr_day",
             "working_hr_week",
             "residence",
             "age_group")

tbl1 <- make_bivariate_tbl(df, "lower_abdominal_pain", ind_var)
tbl2 <- make_bivariate_tbl(df, "lower_back_pain", ind_var)
tbl3 <- make_bivariate_tbl(df, "pain_urination", ind_var)


combined_tbl <- tbl_stack(
  list(tbl1, tbl2, tbl3),
  group_header = c(
    "Lower Abdominal Pain or Discomfort",
    "Lower Back or Flank Pain",
    "Burning or Pain During Urination"
  ), quiet = TRUE
) %>% 
  as_flex_table()

combined_tbl
```


```{r}
doc <- doc %>% 
  body_add_par(value = "Job and Working Hour Related") %>%
  body_add_flextable(value = combined_tbl) %>% 
  body_add_par(value = "")
```






## Odor and Itching Related
```{r}
ind_var <- c("workplace_toilet",
             "absorbent_type",
             "afford_pads",
             "residence")

tbl1 <- make_bivariate_tbl(df, "bloody_urine", ind_var)
tbl2 <- make_bivariate_tbl(df, "vaginal_discharge", ind_var)
tbl3 <- make_bivariate_tbl(df, "vaginal_odor", ind_var)
tbl4 <- make_bivariate_tbl(df, "genital_itching", ind_var)


combined_tbl <- tbl_stack(
  list(tbl1, tbl2, tbl3, tbl4),
  group_header = c(
    "Cloudy dark or bloody urine",
    "Abnormal vaginal discharge",
    "Foul smelling vaginal odor",
    "Genital itching or irritation"
  ),
  quiet = TRUE
) %>%
  as_flex_table()

combined_tbl
```


```{r}
doc <- doc %>% 
  body_add_par(value = "Odor and Itching Related") %>%
  body_add_flextable(value = combined_tbl) %>% 
  body_add_par(value = "")
```






## Menstrual Related
```{r}
ind_var <- c(
  "primary_job",
  "working_hr_day",
  "residence",
  "absorbent_type",
  "workplace_toilet",
  "workplace_water",
  "age_group"
)

tbl1 <- make_bivariate_tbl(df, "menstrual_regularity", ind_var)
tbl2 <- make_bivariate_tbl(df, "pain_severity_score", ind_var)
tbl3 <- make_bivariate_tbl(df, "pain_experience", ind_var)

tbl4 <- make_bivariate_tbl(df, "frequency_of_pain", ind_var)

tbl5 <- make_bivariate_tbl(df, "pain_urination", ind_var)
tbl6 <- make_bivariate_tbl(df, "frequent_urination", ind_var)

tbl4 <- tbl4 %>% as_flex_table

combined_tbl1 <- tbl_stack(
  list(tbl1, tbl2, tbl3),
  group_header = c(
    "Menstrual cycle regularity",
    "Menstrual pain severity score",
    "Menstrual pain experience"
  ),
  quiet = TRUE
) %>%
  as_flex_table()



combined_tbl2 <- tbl_stack(
  list(tbl5, tbl6),
  group_header = c(
    "Burning or pain during urination",
    "Frequent or urgent urination"
  ),
  quiet = TRUE
) %>%
  as_flex_table()

combined_tbl1
combined_tbl2
```
```{r}
table(df$pain_severity_score)


with(df, 
     table(menstrual_regularity) %>% print,
     )
with(df, 
     table(pain_severity_score) %>% print
     )
with(df, 
     table(pain_experience) %>% print
     )


with(df, 
     table(frequency_of_pain) %>% print
     )


with(df, 
     table(pain_urination) %>% print
     )
with(df, 
     table(frequent_urination) %>% print
     )
```


```{r}
doc <- doc %>% 
  body_add_par(value = "Menstrual Related") %>%
  body_add_flextable(value = combined_tbl1) %>% 
  body_add_par(value = "") %>% 
  body_add_flextable(value = tbl4) %>% 
  body_add_par(value = "") %>% 
  body_add_flextable(value = combined_tbl2) %>% 
  body_add_par(value = "")
```



reduced_work = "Missed or reduced work due to menstrual pain"

pain_severity_score = "Menstrual pain severity score"
pain_experience = "Menstrual pain experience"
frequency_of_pain = "Frequency of menstrual pain"
pain_urination = "Burning or pain during urination"
pain_intercourse = "Pain or discomfort during sexual intercourse"

## Job and Working Hour Related
```{r}
ind_var <- c("pain_severity_score",
             "pain_experience",
             "frequency_of_pain",
             "pain_urination",
             "pain_intercourse")

tbl1 <- make_bivariate_tbl(df, "reduced_work", ind_var)




tbl1 <- tbl1 %>% as_flex_table
```


```{r}
doc <- doc %>% 
  body_add_par(value = "Missed or reduced work due to menstrual pain") %>%
  body_add_flextable(value = tbl1) %>% 
  body_add_par(value = "")
```





## Export Document
```{r}
doc %>% 
  print(target = "doc/all_table.docx")
```



